\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-08-18 Latex/paper.tex
Cambios Malliavin
Se añade la sección de Malliavin al articulo.

% custom macros and definitions
\newtheorem{theorem}{Theorem}[section] 
%%\newtheorem{acknowledgement}[theorem]{Acknowledgement} 
%%\newtheorem{algorithm}[theorem]{Algorithm} 
%%\newtheorem{axiom}[theorem]{Axiom} 
%%\newtheorem{case}[theorem]{Case} 
%%\newtheorem{claim}[theorem]{Claim} 
%%\newtheorem{conclusion}[theorem]{Conclusion} 
%%\newtheorem{condition}[theorem]{Condition} 
%%\newtheorem{conjecture}[theorem]{Conjecture} 
\newtheorem{corollary}[theorem]{Corollary} 
%%\newtheorem{criterion}[theorem]{Criterion} 
%%\newtheorem{defi}[theorem]{Definition} 
\newtheorem{example}[theorem]{Example} 
%%\newtheorem{exercise}[theorem]{Exercise} 
%%\newtheorem{hypothesis}[theorem]{Hypothesis} 
\newtheorem{lemma}[theorem]{Lemma} 
%%\newtheorem{notation}[theorem]{Notation} 
%%\newtheorem{problem}[theorem]{Problem} 
\newtheorem{proposition}[theorem]{Proposition} 
%%\newtheorem{question}[theorem]{Question} 
\newtheorem{remark}[theorem]{Remark} 
%%\newtheorem{solution}[theorem]{Solution} 
%%\newtheorem{summary}[theorem]{Summary} 
%%\newtheorem{Rem}[theorem]{Remark}

@@

In the present paper, we find an alternative way to calculate the convexity adjustment for a general interest rate model. The idea is to use the It\^o representation theorem. Unfortunately, the theorem does not give an insight into how to calculate the elements therein. Therefore, it is necessary to introduce basic concepts of Malliavin calculus to apply the Clark-Occone representation formula.

@@

\section{Malliavin}\label{sec:Malliavin}

>>>>

% custom macros and definitions
\newtheorem{theorem}{Theorem}[section] 
%%\newtheorem{acknowledgement}[theorem]{Acknowledgement} 
%%\newtheorem{algorithm}[theorem]{Algorithm} 
%%\newtheorem{axiom}[theorem]{Axiom} 
%%\newtheorem{case}[theorem]{Case} 
%%\newtheorem{claim}[theorem]{Claim} 
%%\newtheorem{conclusion}[theorem]{Conclusion} 
%%\newtheorem{condition}[theorem]{Condition} 
%%\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary} 
%%\newtheorem{criterion}[theorem]{Criterion} 
%%\newtheorem{defi}[theorem]{Definition} 
\newtheorem{example}[theorem]{Example} 
%%\newtheorem{exercise}[theorem]{Exercise} 
%%\newtheorem{hypothesis}[theorem]{Hypothesis} 
\newtheorem{lemma}[theorem]{Lemma} 
%%\newtheorem{notation}[theorem]{Notation} 
%%\newtheorem{problem}[theorem]{Problem} 
\newtheorem{proposition}[theorem]{Proposition} 
%%\newtheorem{question}[theorem]{Question} 
\newtheorem{remark}[theorem]{Remark} 
%%\newtheorem{solution}[theorem]{Solution} 
%%\newtheorem{summary}[theorem]{Summary} 
%%\newtheorem{Rem}[theorem]{Remark}

@@

In the present paper, we find an alternative way to calculate the convexity adjustment for a general interest rate model. The idea is to use the It\^o's representation theorem. Unfortunately, the theorem does not give an insight into how to calculate the elements therein. Therefore, it is necessary to introduce basic concepts of Malliavin calculus to apply the Clark-Ocone representation formula.

@@

\section{Basic introduction to Malliavin calculus}\label{sec:Malliavin}
Malliavin calculus is an infinite-dimensional calculus in a Gaussian space, that is, a stochastic calculus of variations. In other words, this is a theory that provides a way to calculate the derivatives of random variables defined in a Gaussian probability space with respect to the underlying noise. The initial objective of Malliavin was the study of the existence of densities of Wiener functionals such as solutions of stochastic differential equations. But, nowadays, it has become an important tool in stochastic analysis due to the increase in its applications. Some of these applications include stochastic calculus for fractional Brownian motion, central limit theorems for multiple stochastic integrals, and an extension of the Itô formula for anticipative processes, but especially mathematical finance. For example, we can apply Mallaivin calculus for computing hedging strategies, Greeks, or obtain price approximations. See, for example, \cite{AlosLorite} or \cite{Nualart} for more general content.\\

In our case, we are interested in using the Malliavin calculus to apply the Clark–Ocone representation theorem. But, first of all, let's introduce some basic concepts.\\

Now, we introduce the derivative operator in the Malliavin calculus sense and the divergence operator to establish the notation that we use in the remainder of the paper.\\

Consider $W=\left\{W_{t}, t\in \left[0,T\right]\right\}$ a Brownian motion defined on a complete probability space $\left(\Omega, \mathcal{F}, \mathbb{P}\right)$. Let $H=L^{2}(\left[0,T\right])$ and denote by 
\begin{eqnarray*}
W_{t} := \int^{T}_{0} t_{s} \d W_{s},
\end{eqnarray*}
the It\^o integral of a deterministic function $h \in H$, also known as Wiener integral. Let $\mathcal{S}$ be the set of smooth random variables of the form
\begin{eqnarray*}
F=f\left(W_{t_{1}}, \ldots, W{t_{n}}\right)
\end{eqnarray*}
with $t_{1}, \ldots, t_{n} \in \left[0,T\right]$ and $f$ is infinitely differentiable bounded function.

\medbreak

The derivative of a random variable $F$, $D_{s}F$, is defined as the stochastic process given by
\begin{eqnarray*}
D_{s}F = \sum^{n}_{i=1} \frac{\partial f}{\partial x_{i}}\left(W_{t_{1}}, \ldots, W_{t_{n}}\right)1_{\left[0, t_{j}\right]}(s), \hspace{0.4cm} s \in \left[0,T\right].
\end{eqnarray*}

The iterated derivative operator of a random variable $F$ is defined by
\begin{eqnarray*}
D^{m}_{s_{1}, \ldots, s_{m}} F = D_{s_{1}} \cdots D_{s_{m}}F, \hspace{0.4cm} s_{1}, \ldots, s_{m} \in \left[0,T\right].
\end{eqnarray*}

\cite{Nualart} stated that these operators are closable from $L^{p}(\Omega)$ into $L^{p}(\Omega; L^{2}\left[0,T\right])$ for any $p\geq1$, and we denote by $\mathbb{D}^{n,p}$ the closure of $\mathcal{S}$ with respect to the norm
\begin{eqnarray*}
\left\|F\right\|_{n,p} := \left(E\left[F\right]^{p} + \sum^{n}_{i=1} E\left\|D^{i} F\right\|^{p}_{L^{2}\left(\left[0,T\right]^{i}\right)} \right)^{\frac{1}{p}}.
\end{eqnarray*}

\medbreak

We define $\delta$ as the adjoint of derivative operator $D$, also referred to as the Skorohod integral. The domain of $\delta$, denoted by $Dom\text{ }\delta$, is the set of elements $u \in L^{2}([0,T] \times \Omega)$ such that there exists $\delta(u) \in L^{2}(\Omega)$ satisfying the duality relation
\begin{eqnarray*}
E\left[\delta(u) F \right] = E\left[\int^{T}_{0} \left(D_{s} F\right) u_{s} \d s\right].
\end{eqnarray*}

The operator $\delta$ is an extension of the Itô integral in the sense that the set $L^{2}_{a}([0,T] \times \Omega)$ of square integrable and adapted processes is included in $Dom\text{ }\delta$ and the operator $\delta$ restricted to $L^{2}_{a}([0,T] \times \Omega)$ coincides with the Itô stochastic integral.

\medbreak

For any $u \in Dom\text{ }\delta$, we will use the following notation
\begin{eqnarray*}
\delta(u)=\int^{T}_{0}u_{s}\d W_{s}.
\end{eqnarray*}

\medbreak

The representation of functionals of Brownian motion by stochastic integrals, also known as martingale representation, has been widely studied over the years. It states that if $F$ is a square-integrable random variable, there exists a unique adapted process $\varphi$ in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$ such that
\begin{eqnarray*}
F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} \varphi^{i}_{s} dW^{i}_{s}.
\end{eqnarray*}
In other words, there exists a unique martingale representation or, more precisely, the integrand $\varphi$ in the representation exists and is unique in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$.

\medbreak

Unfortunately, it is not easy to find an analytic representation of the process $\varphi$. Here, the Malliavin calculus helps us to find a solution. When the random variable $F$ is Malliavin differentiable, the process $\varphi$ appearing in It\^o's representation theorem, is given by
\begin{eqnarray*}
\varphi^{i}=E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right].
\end{eqnarray*}
In fact,
\begin{eqnarray}
F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right] dW^{i}_{s}
\end{eqnarray}
is the Clark-Ocone representation formula.
